Abstract Binding Trees

### 2015-10-22 paper.tex
Use existing macro
fibration ⇒ opfibration

\newcommand\Grothendieck[2]{\oint^{#1} #2#1}
\newcommand\Pair[2]{\langle #1, #2 \rangle}
\newcommand\Restriction[1]{#1^{*}}
\newcommand\Singleton{\{\bullet\}}

@@

Then, fix a covariant presheaf (copresheaf) of operators
$\Operators:\SCtx\times\Arities\to\Sets$ such that the arrows in $\SCtx$ lift to
renamings of operators' parameters. Via the Grothendieck
construction\footnote{In this case, $C\Grothendieck{}{\Psi}$ represents the
  category of elements of a copresheaf $\Psi : C\to\Sets$ but we keep the $C$
  implicit and simply refer to it as the Grothendieck construction.
  Alternatively, this construction can be understood as a coend
  $C\Grothendieck{}{\Psi} \cong \int^{c \in C}c / C \otimes
  \Discrete{\Psi(c)}$.} $\Grothendieck{}{(-)} : \Sets^{C}\to\Cats$ on operators
we have a category of objects
$\Member{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Grothendieck{}{\Operators}}$
for $\Member{\vartheta}{\Operators\Pair{\Upsilon}{\varrho}}$ and morphisms
$\Hom{\Grothendieck{}{\Operators}}{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Pair{\Pair{\Upsilon'}{\varrho'}}{\vartheta'}}$
for $f : \Pair{\Upsilon}{\varrho}\to\Pair{\Upsilon'}{\varrho'}$ such that
$\EqMember{\Restriction{f}\vartheta}{\vartheta'}{\Operators\Pair{\Upsilon'}{\varrho'}}$.
Equivalently, $\Grothendieck{}{\Operators}$ is the pullback of $\Operators$
along the universal $\Sets$-bundle where $\pi_{\Operators}$ is a discrete
Grothendieck fibration and $ap_{\Singleton}$ is the forgetful functor from pointed sets:

>>>>

\newcommand\Grothendieck[2]{\oint^{#1} #2#1}
\newcommand\Pair[2]{\langle #1, #2 \rangle}
\newcommand\Restriction[1]{#1^{*}}
\newcommand\Singleton{\MkSet{\bullet}}

@@

Then, fix a covariant presheaf (copresheaf) of operators
$\Operators:\SCtx\times\Arities\to\Sets$ such that the arrows in $\SCtx$ lift to
renamings of operators' parameters. Via the Grothendieck
construction\footnote{In this case, $C\Grothendieck{}{\Psi}$ represents the
  category of elements of a copresheaf $\Psi : C\to\Sets$ but we keep the $C$
  implicit and simply refer to it as the Grothendieck construction.
  Alternatively, this construction can be understood as a coend
  $C\Grothendieck{}{\Psi} \cong \int^{c \in C}c / C \otimes
  \Discrete{\Psi(c)}$.} $\Grothendieck{}{(-)} : \Sets^{C}\to\Cats$ on operators
we have a category of objects
$\Member{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Grothendieck{}{\Operators}}$
for $\Member{\vartheta}{\Operators\Pair{\Upsilon}{\varrho}}$ and morphisms
$\Hom{\Grothendieck{}{\Operators}}{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Pair{\Pair{\Upsilon'}{\varrho'}}{\vartheta'}}$
for $f : \Pair{\Upsilon}{\varrho}\to\Pair{\Upsilon'}{\varrho'}$ such that
$\EqMember{\Restriction{f}\vartheta}{\vartheta'}{\Operators\Pair{\Upsilon'}{\varrho'}}$.
Equivalently, $\Grothendieck{}{\Operators}$ is the pullback of $\Operators$
along the universal $\Sets$-bundle where $\pi_{\Operators}$ is a discrete
Grothendieck opfibration and $ap_{\Singleton}$ is the forgetful functor from pointed sets:
